---
title: "Candidate Mentions"
author: "Kate Stohr"
date: "January 6, 2016"
output: html_document
---
Candidate mentions provided by Daniel Mclaughlin 2015-01-05.

https://fusionnetwork.slack.com/files/daniel.mclaughlin/F0HM7BEG3/candidates_mentioning_candidates.csv

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(ggparallel)
```

###Load data

```{r message=FALSE, warning=FALSE}
scrapestatus<-read.csv("data/2016_01_08_scraping_status.csv", check.names=TRUE)
cmc<-read.csv("data/2016_01_05_candidates_mentioning_candidates.csv")
```

###Process Data 

```{r message=FALSE, warning=FALSE}

# remove noncandidates 
cmc<-filter(cmc, target!="joebiden")
rm
# assign source names to candidates by acct
# assign source party affiliation 
dim(cmc) #get dims of original data
labels<-select(scrapestatus, Name, Party.Affiliation, Twitter)
names(labels)<-c("source_name", "source_party", "source_account")
labels$source_account<-tolower(labels$source_account)
cmc<-left_join(cmc, labels, by =c("source" = "source_account"))
dim(cmc) #check dims
```

```{r message=FALSE, warning=FALSE}
# assign target names to candidates by acct
# assign target party affiliation 
names(labels)<-c("target_name", "target_party", "target_account")
cmc<-left_join(cmc, labels, by =c("target" = "target_account"))
dim(cmc) #check dims 

```

```{r message=FALSE, warning=FALSE}
#Filter data to exclude observations of candidates mentioning themselves 
c_at_c<-cmc[cmc$source_name != cmc$target_name, ]
dim(c_at_c) #check dims
```

###Explore Data
```{r message=FALSE, warning=FALSE}
tot_mentions<-sum(c_at_c$mentions)
tot_mentions

#Get table of mentions by source in descending order
src_agg<-aggregate(mentions ~ source_name, data=c_at_c, sum)
src_agg_sorted<-arrange(src_agg, desc(mentions))
head(src_agg_sorted)
tail(src_agg_sorted)

#Get table of mentions by target in descending order
trg_agg<-aggregate(mentions ~ target_name, data=c_at_c, sum)
trg_agg_sorted<-arrange(trg_agg, desc(mentions))
head(trg_agg_sorted)
tail(trg_agg_sorted)

#Get table of mentions by source_party in descending order
src_party<-aggregate(mentions ~ source_party, data=c_at_c, sum)
src_party

#Get table of mentions by target_party in descending order
trg_party<-aggregate(mentions ~ target_party, data=c_at_c, sum)
trg_party
```

##Candidate share of mentions by source party 
```{r message=FALSE, warning=FALSE}
top_trg_byparty<-aggregate(mentions ~ target_name + source_party, data=c_at_c, sum)
top_trg_byparty<-arrange(top_trg_byparty, desc(mentions))

top_trg_byparty$source_party<-relevel(top_trg_byparty$source_party, ref="Republican")

share<-ggplot(data=top_trg_byparty, aes(y=mentions, x=reorder(target_name, mentions),
                               fill=source_party)) +
        geom_bar(stat="identity",
                 position=position_dodge())+
        coord_flip()+
        xlab("candidate")+
        ylab("number of mentions")+
        ggtitle("Candidates Tagged by Other Candidates")+
        labs(fill = "Source of tag (by party)")+
        theme_minimal()
share
```

Candidates mentioned other candidates `r tot_mentions` times. 

## 5 Most Catty Candidates
```{r message=FALSE, warning=FALSE}
#Subset top 5 candidates with most mentions to their name. 
most_catty<-src_agg_sorted$source_name[1:5]
most_catty_subset<-filter(c_at_c, source_name %in% most_catty)
##write.csv(most_catty_subset, file = "data/max_5_catty_data.csv")
```


```{r message=FALSE, warning=FALSE}
#plot catty candidates
max_catty<-ggparallel(
        vars = list("source_name", "target_name"),
        data=most_catty_subset, 
        method = "parset", 
        weight = "mentions", 
        order = 1, 
        text.angle = 360, 
        alpha =.5,
        label.size = 6,
        )+ 
        theme(legend.position="none")
max_catty
```

## 5 Least Catty Candidates
```{r message=FALSE, warning=FALSE}
#Subset top 5 candidates with least mentions to their name. 
src_agg_asc<-arrange(src_agg, mentions)
least_catty<-src_agg_asc$source_name[1:5]
least_catty_subset<-filter(c_at_c, source_name %in% least_catty)
##write.csv(least_catty_subset, file = "data/min_5_catty_data.csv")
```

```{r message=FALSE, warning=FALSE}
min_catty<-ggparallel(
        vars = list("source_name", "target_name"),
        data=least_catty_subset, 
        method = "parset", 
        weight = "mentions", 
        order = -1, 
        text.angle = 360, 
        alpha =.5,
        label.size = 6, 
        )+ 
        theme(legend.position="none")
min_catty
```

## Top 5 Most Narcissistic 

```{r message=FALSE, warning=FALSE}
#filter mentions of candidates targeting themselves
c_at_self<-cmc[cmc$source_name == cmc$target_name, ]
c_at_self_sorted<-arrange(c_at_self, desc(mentions))
##write.csv(c_at_self_sorted, file = "data/max_narcissits_data.csv")
```

```{r message=FALSE, warning=FALSE}
narcissits<-ggparallel(
        vars = list("source_name", "target_name"),
        data=c_at_self_sorted[1:5,], 
        method = "parset", 
        weight = "mentions", 
        order = 1, 
        text.angle = 360, 
        alpha =.5,
        label.size = 6 
        )+
        theme(legend.position="none")
narcissits
```

## Tables for info graphics 
###Candidates who tagged other candidates the most
```{r}
mention_agg<-aggregate(mentions ~ target_name, data=most_catty_subset, sum)
mention_agg

tot_mention_agg<-aggregate(mentions~ target_name, data=c_at_c, sum)

identical(sum(tot_mention_agg$mentions), tot_mentions)

per_tot<-sum(mention_agg$mentions)/sum(tot_mention_agg$mentions)

per_tot

src_mention_agg<-aggregate(mentions ~ source_name, data=most_catty_subset, sum)

src_mention_agg
```

###Candidates who tagged other candidates the most
```{r}
least_mention_agg<-aggregate(mentions ~ target_name, data=least_catty_subset, sum)
least_mention_agg

least_per_tot<-sum(least_mention_agg$mentions)/sum(tot_mention_agg$mentions)

least_per_tot

least_src_mention_agg<-aggregate(mentions ~ source_name, data=least_catty_subset, sum)

least_src_mention_agg
```

###Candidates who tagged themselves the most

```{r}
c_at_self_sorted[1:5, c(4,3)]

narc_per_tot<-sum(least_mention_agg$mentions)/sum(tot_mention_agg$mentions)

```

